---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height = 4,
  fig.width = 9,
  out.width = "100%",
  dpi = 300
)
if (!interactive()) {
  options(width = 99)
}
```

# predmark

<!-- badges: start -->
[![Lifecycle: experimental][life_badge]][life_link]
[![CRAN status][cran_badge]][cran_link]
[![Codecov test coverage][cov_badge]][cov_link]
[![R build status][ga_badge]][ga_link]
<!-- badges: end -->

This package contains data and documentation from prediction markets and
forecasting models for the 2018 and 2020 U.S. elections. The data is formatted
in ways to facilitate statistical comparison. This package was built to both
hold the data and make for easy installation, including package dependencies
needed to completely replicate the data formatting.

The [original repository][mm] for this project was not formatted as a package.

## Installation

You can install the development version of predmark from [GitHub][gh] with:

```{r install, eval=FALSE}
# install.packages("remotes")
remotes::install_github("kiernann/predmark")
```

## Data

```{r library}
library(tidyverse)
library(predmark)
```

The package contains daily predictions from PredictIt and FiveThirtyEight.

```{r markets18}
markets18
```

```{r model18}
model18
```

<!-- refs: start -->
[life_badge]: https://img.shields.io/badge/lifecycle-experimental-orange.svg
[life_link]: https://www.tidyverse.org/lifecycle/#maturing
[cran_badge]: https://www.r-pkg.org/badges/version/predmark
[cran_link]: https://CRAN.R-project.org/package=predmark
[ga_badge]: https://github.com/kiernann/predmark/workflows/R-CMD-check/badge.svg
[ga_link]: https://github.com/kiernann/predmark/actions
[cov_badge]: https://codecov.io/gh/kiernann/predmark/branch/master/graph/badge.svg
[cov_link]: https://codecov.io/gh/kiernann/predmark?branch=master
[mm]: https://github.com/kiernann/models-markets
[gh]: https://github.com/kiernann/predmark
<!-- refs: end -->
